### 2019-02-05 reports/thesis/chapters/5_inference.tex
Figure export for NullIid, deleted Mixture2

>>>>

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullMean.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullMean.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullMean.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullMean.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{Different types of central tendency estimators were used on $\pi r^2$ $\normal(0,1)$ random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_nullStd.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_nullStd.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_nullStd.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_nullStd.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{Different types of statistical dispersion estimators were used on $\pi r^2$ $\normal(0,1)$ random variables. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zMean.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zMean.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zMean.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zMean.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators. Shown are the mean of the normalised random variables. The dotted lines show the 95\% confidence interval for the sample mean. The box plots represent 100 repeats of the simulation.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zStd.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zStd.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zStd.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zStd.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators. Shown are the standard deviation of the normalised random variables. The dotted lines show the 95\% confidence interval for the sample variance. The box plots represent 100 repeats of the simulation.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidEmpirical_zKurtosis.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMadMode_zKurtosis.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMeanVar_zKurtosis.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMedianIqr_zKurtosis.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{$\pi r^2$ $\normal(0,1)$ random variables were simulated and then normalised using the different types of estimators. Shown are the sample kurtosis of the normalised random variables. The dotted lines show the 95\% confidence interval for the sample kurtosis. The box plots represent 100 repeats of the simulation.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullMean.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullMean.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullMean.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullMean.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{Different types of central tendency estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample mean.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureEmpirical_nullStd.eps}
				\caption{Empirical null}
			\end{subfigure}
			\begin{subfigure}[b]{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMadMode_nullStd.eps}
				\caption{MAD mode null}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMeanVar_nullStd.eps}
				\caption{Mean variance null}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/NullIid/NullIidMixtureMedianIqr_nullStd.eps}
				\caption{Median IQR null}
			\end{subfigure}
		}
	\caption{Different types of statistical dispersion estimators were used on $\pi r^2$ mixture of Gaussian random variables. The random variable has distribution $\normal(0,1)$ with probability $0.9$ and $\normal(3,1)$ with probability $0.1$. Shown are the sampling distributions from 100 repeats. The dotted lines show the 95\% confidence interval for the sample variance.}
\end{figure}
